
\documentclass[preprint,12pt]{elsarticle}

\usepackage{amssymb}

\usepackage{lineno}
\journal{Chess League - Zeyecx}


\begin{document}
	
\begin{frontmatter}
			
\title{Chess League}
		
		
\author{Zeyecx, Donbur, Jonny}
		
\address{German Paper}
	 
\begin{abstract}
	The idea is to develop a chess tournament in which teams of different streamers play against each other.
	This will first be done in a group system which will later be replaced by a knockout system. 
\end{abstract}
\end{frontmatter}

\section{Team structure}
The teams consist of 6 players per team. These must be a active viewer of the respective streamer. 
The game is played in different rating groups (1000, 1400, 1800, 2000, 2200, Streamer).

\section{Rating groups}

The rating groups are:
\begin{itemize}
	\item 1000
	\item 1400 
	\item 1600
	\item 1800
	\item 2000
	\item 2200
\end{itemize}
If there is a tie, the two streamers play against each other. If they do not want to do this, they can appoint a sub to play in their place.

\section{Time managment}
The streamers have 2 weeks to find a date in the group phase. The dates for the knockout phase will be announced separately.
The streamers have to register for the event in advance. Then they get 1 week to set up their team.
Then the event starts.
All matches must be streamed.
However, since we have no registrations, the schedules will be announced elsewhere.


\section{Anhang}
This is a basic version. We reserve the right to make further changes.



\bibliographystyle{./template/model1-num-names}

\end{document}
